Draft

### 2022-06-20 Final/FinalReport.qmd
adjustments to variable types in dataset, small edits to recipes

```{r filter-data}
abortion_data <- abortion_data_full %>% 
  filter(year >= "1995") %>%
  select(-starts_with("wave"), -starts_with("wvsccode"))
```

@@

```{r recipe1}
abortion_rec1 <- recipe(aj ~ year + ideology + cai + godimportant +
                        respectauthority, nationalpride,
                        data = abortion_data) %>%
  step_center(year) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors())

@@

```{r recipe2}
abortion_rec2 <- recipe(aj ~ year + godimportant,
                        data = abortion_data) %>%
  step_center(year) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors())

@@

```{r recipe3}
abortion_rec3 <- recipe(aj ~ year + ideology + cai + nationalpride,
                        data = abortion_data) %>%
  step_center(year) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors())

@@

```{r ci}
tidy(abortion_fit1, conf.int = TRUE) %>%
  kable(digits = 3)
tidy(abortion_fit2, conf.int = TRUE) %>%
  kable(digits = 3)
tidy(abortion_fit3, conf.int = TRUE) %>%
  kable(digits = 3)
```

We then proceed to our hypothesis test. As stated in our introduction, given that this issue has become highly polarized by political party, we suspect that liberal political attitudes will correlate with belief that abortion is more justified, leading to the following hypotheses.

@@

```{r predict}
abortion_training_pred1 <- predict(abortion_fit1, abortion_training) %>%
  bind_cols(abortion_training %>% select(aj, year, ideology, cai, 
                                         godimportant, respectauthority, 
                                         nationalpride))
abortion_training_pred1

abortion_training_pred2 <- predict(abortion_fit2, abortion_training) %>%
  bind_cols(abortion_training %>% select(aj, year, godimportant))
abortion_training_pred2

abortion_training_pred3 <- predict(abortion_fit3, abortion_training) %>%
  bind_cols(abortion_training %>% select(aj, year, ideology, cai, 
                                         nationalpride))
abortion_training_pred3
```

>>>>

```{r filter-data}
abortion_data <- abortion_data_full %>% 
  filter(year >= "1995") %>%
  select(-starts_with("wave"), -starts_with("wvsccode"))

abortion_data$year <- as.factor(abortion_data$year)
abortion_data$respectauthority <- as.factor(abortion_data$respectauthority)
abortion_data$respectauthority <- factor(abortion_data$respectauthority, levels=c('0', '-1', '1'))
abortion_data$nationalpride <- as.factor(abortion_data$nationalpride)
```

@@

```{r recipe1}
abortion_rec1 <- recipe(aj ~ year + ideology + cai + godimportant +
                        respectauthority + nationalpride,
                        data = abortion_data) %>%
  step_center(ideology) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors())

@@

```{r recipe2}
abortion_rec2 <- recipe(aj ~ year + godimportant,
                        data = abortion_data) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors())

@@

```{r recipe3}
abortion_rec3 <- recipe(aj ~ year + ideology + cai + nationalpride,
                        data = abortion_data) %>%
  step_center(ideology) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors())

@@

```{r inference}
tidy(abortion_fit1, conf.int = TRUE) %>%
  kable(digits = 3)
```

We then proceed to our hypothesis test. As stated in our introduction, given that this issue has become highly polarized by political party, we suspect that liberal ideology and political attitudes will correlate with belief that abortion is more justified, leading to the following hypotheses:

@@

```{r predict}
abortion_training_pred1 <- predict(abortion_fit1, abortion_training) %>%
  bind_cols(abortion_training %>% select(aj, year, ideology, cai, 
                                         godimportant, respectauthority, 
                                         nationalpride))
abortion_training_pred1
```
